%-------------------------
% Resume in Latex
% Credits : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% % Hyperlink Setup

% \usepackage{hyperref}
% \hypersetup{
%     colorlinks=true,
%     linkcolor=blue,
%     filecolor=magenta,      
%     urlcolor=blue,
% }

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
       #3 & \small #4 \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\projectsSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}

\newcommand{\resumeJobRole}[1]{\small{#1}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{ \vspace{-6pt} \begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-9pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Rahul Pande}}
  &
%   \faEnvelope
  \space \href{mailto:rspande@wpi.edu}{rspande@wpi.edu}\\
  
%   \href{https://github.com/rahul-pande}{github.com/rahul-pande} $\vert$
  \href{http://rahulpande.me/?utm_source=organic&utm_medium=resume&utm_campaign=intership_spring_2019}{rahulpande.me}
  $\vert$
  \href{http://www.linkedin.com/in/pande-rahul}{linkedin.com/in/pande-rahul}
  
  &
%   \faPhone
  \space\space\space\space\space\space\space 508-333-9986 \\
\end{tabular*}


% --------OBJECTIVE--------------------
\section{Objective}
\begin{flushleft}
{Seeking internship and co-op opportunities for Fall 2019 in the field of Data Science with a focus in Deep Learning and Machine Learning}
\end{flushleft}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Worcester Polytechnic Institute (WPI)}{Worcester, MA}
      {Master of Science in Data Science GPA: 3.83/4.0}{May 2020}
    \resumeSubheading
      {Vishwakarma Institute of Technology (VIT, Pune)}{Pune, India}
      {Bachelor of Technology in Electronics and Telecommunication GPA: 8.59/10}{May 2015}
  \resumeSubHeadingListEnd

% -------------COURSES----------------
\section{Courses}
 
 \textbf{WPI:}{ Deep Learning, Big Data Management, Statistical Learning }
 \hfill
 \textbf{VIT:}{ Pattern Recognition, Linear Algebra }

% --------------SKILLS----------------
\section{Skills}
 
 \textbf{Programming:} {Python, R, SQL, Java }
 \hfill
 \textbf{Technologies:}{ Hadoop, Postgres, Tableau, AWS, MongoDB, D3 }
 \newline
 \textbf{Packages:}{ scikit-learn, numpy, scipy, pandas, matplotlib, ggplot2, dplyr, caret, Dask, Tensorflow }
 
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Researcher (Independent Study)}{Cambridge, MA}
      {Takeda Pharmaceutical} {January 2019 - May 2019}
      
      \resumeJobRole {}
    %   {Analysis of data gathered by wearable sensors for Human Activity Recognition (HAR)}
      \resumeItemListStart
        \resumeItem {}
        {Explored the UCI HAR actigraphy dataset and implemented various architectures of CNN and LSTM to classify 6 different human activities based on measurements captured by wearable sensors and achieved \textbf{f1 score of 0.97}}
        \resumeItem {}
        {Large scale deep learning on UK Biobank actigraphy and phenotype dataset comprised of 500K subjects}
        \resumeItem {}
        {Achieved 34.8 rmse and f1 score of .78 in predicting age and insomnia respectively from the actigraphy data using Multitask Learning with Deep Neural Networks}
      \resumeItemListEnd
      
    \resumeSubheading
      {Lab Assistant at Academic and Research Computing}{Worcester, MA}
      {WPI} {August 2018 - Present}
      
      \resumeJobRole
      {Developing and maintaining the website for Northeast Cyberteam (NSF Award Number: 1659377) to improve its ease of use (\href{https://necyberteam.org/user/164}{necyberteam.org})}

    \resumeSubheading
      {Product Analyst} {Pune, India} 
      {Vuclip India Pvt. Ltd.} {April 2016 - June 2018}
      
      \resumeJobRole
      {Set up analytic processes and frameworks, and helped improve user engagement on the platform through effective use of machine learning.}

      \resumeItemListStart
        \resumeItem{Complaints Prediction:}
          {Developed a Random Forest model to predict if a user will complain (cross-validation test recall of 0.79). Decreased complaints from 11\% to 7\% avoiding hefty penalties.}
        \resumeItem{Content Recommendation:}
          {Formed user clusters (k-prototype) based on the type and amount of content consumption and then recommended content based on collaborative filtering.}
        \resumeItem{Analytics:}
          {Holistic content performance analytics related to Original Series content at Vuclip. Mining market data to improve content production/acquisition strategy.}
        \resumeItem{Data Engineering:}
          {Authored numerous Apache Airflow data pipelines to replace cron scripts which significantly reduced database locks, failures and execution time. Improved workload management on multiple servers.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \projectsSubItem{Music Generation with Neural Nets \normalfont{(WPI $\vert$ March 2019):}}
      {Generated synthetic music sequences (MIDI notes) using LSTM and GAN and outperformed $\sqrt{n}$ randomized real sequences}
    \projectsSubItem{Blind Source Separation \normalfont{(WPI $\vert$ December 2018):}}
      {Separating mixed audio signals using Non-negative Matrix Factorization (NMF).}
    \projectsSubItem{Website Insights \normalfont{(Vuclip $\vert$ 2017):}}
      {Get insights on a web forum using Scrapy, NLTK and, D3.}
    \projectsSubItem{Android Development \normalfont{(Personal $\vert$ 2013):}}
      {Developed the official Android Application for VIT, Pune. Second rank in on-spot android app development competition.}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
